{\bf {\Large Improving estimates of ecosystem metabolism computed from dissolved oxygen time series}}

### 2014-11-04 swmp_noise.Rnw
mcm revisions v2, still need to revise intro
some edits from Jim's comments, windows specific to each case study

% aliased citations
\defcitealias{BeckIR}{Beck and Hagy, In review}
\defcitealias{CDMO14}{CDMO 2014}
\defcitealias{RDCT14}{RDCT 2014}

@@

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-02-01','2012-02-14')) 
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

@@

% plots of summarized metabolism estimates, before/after detiding
% ELKVM, PDBBY
\centering\vspace*{\fill}
<<metab_sum1, cache = T, eval = T, echo = F, fig.height = 5.5, fig.width = 7, fig.cap = 'Means and standard errors of daily metabolism estimates (gross production, total respiration) aggregated by month and season.  Aggregated estimates are for Elkhorn Slough and Padilla Bay from observed and filtered \\ac{DO} time series.'>>=

# load metabolism data
load('met_ls.RData')

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))

met_sub <- met_ls[grep(sel_vec, names(met_ls))]

@@

    # add week, month cols
    x$Week <- format(x$Date, '%W')
    x$Month <- format(x$Date, '%m')

    # seas col
    x$Season <- car::recode(x$Month, "c('01','02','03') = 'W'; 
      c('04','05','06') = 'Sp'; 
      c('07','08','09') = 'Su'; 
      c('10','11','12') = 'F'")

@@

# aggregate by weekly, monthly, seasonal categories
# for each case...
agg_sum <- llply(met_sub, 
  .fun = function(x){

@@

    # melt by weekly, monthly, seasonal cats
    # change here for cats to includes
    x <- melt(x, measure.var = c('Month', 'Season'),
      id.var = c('Date', met_cols)
      )

    agg_res <- dlply(x,
      .var = c('variable'), 
      .fun = function(y){

@@

          tmp <- summarySE(y, measurevar = met, groupvars = 'value',
            narm = T) 
          names(tmp)[names(tmp) %in% met] <- 'mean'
          out[[met]] <- tmp

@@

        # combine metabolism categories 
        out <- melt(out, id.var = names(out[[1]]))
        names(out)[names(out) %in% 'L1'] <- 'var'
        out

@@

    # combine time categories
    agg_res <- melt(agg_res, id.var = names(agg_res[[1]]))
    names(agg_res)[names(agg_res) %in% 'L1'] <- 'cats'

@@

@@

to_plo <- melt(agg_sum, id.var = names(agg_sum[[1]]))

# reassign factor labels
to_plo$value <- factor(to_plo$value, levels = c('01', '02', '03', '04',
  '05', '06', '07', '08', '09', '10', '11', '12', 'W', 'Sp', 'Su', 'F'), 
  labels = c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',' 12',
    'W', 'Sp', 'Su', 'F')
  )
to_plo$var <- factor(to_plo$var, levels = c('Pg', 'Rt', 'NEM'), 
  labels = c('Pg', 'Rt', 'NEM'))
to_plo$sub_var <- factor(to_plo$sub_var, levels = c('dtd', 'obs'), 
  labels = c('Filtered', 'Observed'))
to_plo$L1 <- gsub('_wtreg_[0-9]*.RData$', '', to_plo$L1)
to_plo$L1 <- factor(to_plo$L1, 
  levels = c('ELKVM', 'PDBBY', 'RKBMB', 'SAPDC'),
  labels = c('Elkhorn Slough', 'Padilla Bay', 'Rookery Bay', 
    'Sapelo Island')
  )

@@

ylab <- expression(paste('g ', O [2], ' ', m^-2, d^-1))
for(site in 1:2){

  sub_plo <- to_plo[to_plo$L1 %in% levels(to_plo$L1)[site], ]

  p <- ggplot(sub_plo, aes(x = factor(value), y = mean, group = sub_var,
      colour = sub_var)) +
    geom_line() +
    geom_point() + 
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
      width=.3) +
    facet_wrap(cats ~ var, scales = 'free') +
    theme_bw() +
    scale_y_continuous(ylab) + 
    scale_x_discrete(name = element_blank()) +
    theme(
      legend.position = 'top',
      legend.title = element_blank(),
      plot.margin= unit(rep(0, 4), "lines"),
      axis.text = element_text(size = 8)
      ) +
    ggtitle(levels(to_plo$L1)[site])

  assign(paste0('p', site), p)

# get common legend, remove from p1
mylegend <- g_legend(p1)
p1 <- p1 + theme(legend.position = 'none')
p2 <- p2 + theme(legend.position = 'none')

# final plot
grid.arrange(
  mylegend,   
  arrangeGrob(p1, p2, ncol = 1),
  ncol = 1, heights = c(1,10)
  )

% RKBMB, SAPDC
% plots of summarized metabolism estimates, before/after detiding
\centering\vspace*{\fill}
<<metab_sum2, cache = T, eval = T, echo = F, fig.height =5.5, fig.width = 7, fig.cap = 'Means and standard errors of daily metabolism estimates (gross production, total respiration) aggregated by month and season.  Aggregated estimates are for Rookery Bay and Sapelo Island from observed and filtered \\ac{DO} time series.  May was removed from Rookery Bay because of incomplete data.'>>=

# load metabolism data
load('met_ls.RData')

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))

met_sub <- met_ls[grep(sel_vec, names(met_ls))]

    # add week, month cols
    x$Week <- format(x$Date, '%W')
    x$Month <- format(x$Date, '%m')

    # seas col
    x$Season <- car::recode(x$Month, "c('01','02','03') = 'W'; 
      c('04','05','06') = 'Sp'; 
      c('07','08','09') = 'Su'; 
      c('10','11','12') = 'F'")

# aggregate by weekly, monthly, seasonal categories
# for each case...
agg_sum <- llply(met_sub, 
  .fun = function(x){

    # melt by weekly, monthly, seasonal cats
    # change here for cats to includes
    x <- melt(x, measure.var = c('Month', 'Season'),
      id.var = c('Date', met_cols)
      )

    agg_res <- dlply(x,
      .var = c('variable'), 
      .fun = function(y){

          tmp <- summarySE(y, measurevar = met, groupvars = 'value',
            narm = T) 
          names(tmp)[names(tmp) %in% met] <- 'mean'
          out[[met]] <- tmp

        # combine metabolism categories 
        out <- melt(out, id.var = names(out[[1]]))
        names(out)[names(out) %in% 'L1'] <- 'var'
        out

    # combine time categories
    agg_res <- melt(agg_res, id.var = names(agg_res[[1]]))
    names(agg_res)[names(agg_res) %in% 'L1'] <- 'cats'

to_plo <- melt(agg_sum, id.var = names(agg_sum[[1]]))

# reassign factor labels
to_plo$value <- factor(to_plo$value, levels = c('01', '02', '03', '04',
  '05', '06', '07', '08', '09', '10', '11', '12', 'W', 'Sp', 'Su', 'F'), 
  labels = c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',' 12',
    'W', 'Sp', 'Su', 'F')
  )
to_plo$var <- factor(to_plo$var, levels = c('Pg', 'Rt', 'NEM'), 
  labels = c('Pg', 'Rt', 'NEM'))
to_plo$sub_var <- factor(to_plo$sub_var, levels = c('dtd', 'obs'), 
  labels = c('Filtered', 'Observed'))
to_plo$L1 <- gsub('_wtreg_[0-9]*.RData$', '', to_plo$L1)
to_plo$L1 <- factor(to_plo$L1, 
  levels = c('ELKVM', 'PDBBY', 'RKBMB', 'SAPDC'),
  labels = c('Elkhorn Slough', 'Padilla Bay', 'Rookery Bay', 
    'Sapelo Island')
  )

# remove may from Rookery Bay, lots of missing data
to_plo[to_plo$L1 %in% 'Rookery Bay'  & to_plo$value %in% '5', c('mean', 'sd', 'se', 'ci')] <- NA

ylab <- expression(paste('g ', O [2], ' ', m^-2, d^-1))
for(site in 3:4){

  sub_plo <- to_plo[to_plo$L1 %in% levels(to_plo$L1)[site], ]

  p <- ggplot(sub_plo, aes(x = factor(value), y = mean, group = sub_var,
      colour = sub_var)) +
    geom_line() +
    geom_point() + 
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
      width=.3) +
    facet_wrap(cats ~ var, scales = 'free') +
    theme_bw() +
    scale_y_continuous(ylab) + 
    scale_x_discrete(name = element_blank()) +
    theme(
      legend.position = 'top',
      legend.title = element_blank(), 
      plot.margin= unit(rep(0, 4), "lines"),
      axis.text = element_text(size = 8)
      ) +
    ggtitle(levels(to_plo$L1)[site])

  assign(paste0('p', site), p)

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

# get common legend, remove from p1
mylegend <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')
p4 <- p4 + theme(legend.position = 'none')

# final plot
grid.arrange(
  mylegend,   
  arrangeGrob(p3, p4, ncol = 1),
  ncol = 1, heights = c(1,10)
  )

@@

@@

@@

#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)

@@

#     do_dtd <- with(dat_in, 
#       cor.test(DO_nrm, Tide)

@@

@@

#     # as list for all metab correlations

@@

#     met_cor <- list(

@@

#       Pg_obs = with(dat_in, 
#         cor.test(Pg, sunrise)
#         ),

@@

#       Rt_obs = with(dat_in, 
#         cor.test(Rt, sunset)
#         ),
#       NEM_obs = with(dat_in, 
#         cor.test(NEM, daytot)
#         ),
#       Pg_dtd = with(dat_in, 
#         cor.test(Pg_dtd, sunrise)
#         ),
#       Rt_dtd = with(dat_in, 
#         cor.test(Rt_dtd, sunset)
#         ),
#       NEM_dtd = with(dat_in, 
#         cor.test(NEM_dtd, daytot)

@@

@@

#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       met_cor)

@@

#     # convert the stats for each wtreg to data frame
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#     names(res_sum) <- c('var', 'cor', 'pval')

@@

@@

# # melt and make separate columns for site and window comb value
# cor_res <- melt(cor_res, id.var = names(cor_res[[1]]))  
# cor_res$site <- gsub('_wtreg_[0-9]*.RData', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_|.RData', '', cor_res$L1))

@@

@@

# cor_res$sub_var <- gsub('^.*_', '', cor_res$var)

@@

# save(cor_res, file = 'cor_res.RData')
# to_plo <- cor_res
# to_plo$group_var <- paste(to_plo$Tide, to_plo$sub_var)
# to_plo_obs <- to_plo[to_plo$sub_var %in% 'obs', ]
# p1 <- ggplot(to_plo[to_plo$sub_var %in% 'dtd',], 
#     aes(x = dec_time, y = cor, colour = Tide, group = group_var)) +
#   geom_line() + 
#   geom_line(data = to_plo_obs, 
#     aes(x = dec_time, y = cor, group = group_var), 
#     colour = 'black', size = 1) +
#   geom_point(aes(pch = sub_var)) +
#   facet_grid(hour ~ site + var) +
#   ylim(c(-1, 1))

@@

# subset cor_res for window of 30 days, tidal prop 1
cor_res <- cor_res[with(cor_res, dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]), ]

# make wide form
to_tab <- dcast(cor_res, site + sub_var ~ var, value.var = 'cor')

@@

# p vals for each correlation
pvals <- dcast(cor_res, site + sub_var ~ var, value.var = 'pval')

# reorder rows, columns for plot
pvals$sub_var <- factor(pvals$sub_var, levels = c('obs', 'dtd'))
pvals <- pvals[with(pvals, order(site, sub_var)), ]
pvals <- pvals[, c('site', 'sub_var', 'do', 'Pg', 'Rt', 'NEM')]

# combine both tables
tab <- to_tab
rows <- as.character(tab$site)
tab <- form_fun(tab[, -c(1:2)])
pvals <- pvals[, -c(1:2)]
pdims <- dim(pvals)

pvals <- star_fun(c(as.matrix(pvals)))
tab <- c(as.matrix(tab))
tab <- paste0(tab, pvals)
tab <- matrix(tab, nrow = pdims[1], ncol = pdims[2])

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after (filtered) filtering with weighted regression.  \\ac{DO} values are correlated with predicted tidal height at each observation, whereas metabolism estimates are correlated with mean tidal height change between observations during day, night, or total day periods for production, respiration, and net metabolism, respectively.'

foot.val<-'\\footnotesize *$p<0.05$; **$p<0.01$; ***$p<0.001$\\\\\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism'

@@

% case study metabolism results, including perc anom
<<case_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# # metab estimates for each wtreg
# load('met_ls.RData')
# 
# met_comp <- ldply(met_ls, function(x){
#   
#   # detided
#   anoms <- anoms.fun(x, pgvar = 'Pg_dtd', rtvar = 'Rt_dtd')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg_dtd', 'Rt_dtd', 'NEM_dtd')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   dtd <- rbind(anoms, sums)
#   dtd$X1 <- gsub('_dtd', '', dtd$X1)
#   dtd$Input <- 'Detided'
#   
#   # observed
#   anoms <- anoms.fun(x, pgvar = 'Pg', rtvar = 'Rt')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg', 'Rt', 'NEM')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   obs <- rbind(anoms, sums)
#   obs$Input <- 'Observed'  
#   
#   # output
#   out <- rbind(dtd, obs)
#   names(out) <- c('Metab', 'Metric', 'Value', 'Input')
#   
#   return(out)
#   
#   })
#
# 
# # subset metab estimates windows that were used
# load('case_grds.RData')
# sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))
# 
# met_comp <- met_comp[grep(sel_vec, met_comp$.id),]
# 
# save(met_comp, file = 'met_comp.RData')

@@

@@

# make columns as factors for correct row, column order w/ dcast
to_tab$Input <- factor(to_tab$Input, levels = c('Observed', 'Filtered'))
to_tab$Metab <- factor(to_tab$Metab, levels = c('Pg', 'Rt', 'NEM'))
to_tab$Metric <- factor(to_tab$Metric, levels = c('Avg', 'se', 'Anom'))

@@

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism' 
latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = unique(to_tab$Site),
  n.rgroup = rep(2, 4),
  cgroup = c('Pg\\textsuperscript{\\textit{a}}', 'Rt', 'NEM'),
  n.cgroup = c(3, 3, 2),
  rowname = rows,
  colheads=c(rep(c('Mean','Std. Err.', 'Anom'),2), c('Mean', 'Std. Err.')),
  label = 'tab:case_res'
  )
@
\clearpage

>>>>

% aliased citations
\defcitealias{BeckIR}{Beck and Hagy, In review}
\defcitealias{CDMO14}{CDMO 2014}
\defcitealias{NRC00}{NRC 2000}
\defcitealias{RDCT14}{RDCT 2014}

@@

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-02-01','2012-02-14')) 
sel_vec <- with(case_grds, which(dec_time == casewins[['SAPDC']][[1]] & hour == casewins[['SAPDC']][[2]] & Tide == casewins[['SAPDC']][[3]]))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

@@

% plots of summarized metabolism estimates, before/after detiding
% all case studies
\centering\vspace*{\fill}
<<metab_sum, cache = T, eval = T, echo = F, cache = T, fig.height = 5.5, fig.width = 7, fig.cap = 'Means and standard errors of daily metabolism estimates (gross production, total respiration) aggregated by month.  Aggregated estimates are shown for observed and filtered \\ac{DO} time series.  May was removed from Rookery Bay because of incomplete data.'>>=

# load metabolism dataa
load('met_ls.RData')

# subset metab estimates by window widhts for each case study
load('case_grds.RData')
sel_vec <- llply(
  casewins, 
  .fun = function(x) with(case_grds, which(dec_time == x[[1]] & hour == x[[2]] & Tide == x[[3]]))
)
sel_vec <- paste0(names(casewins), '_wtreg_', unlist(sel_vec), '.RData')
met_sub <- met_ls[names(met_ls) %in% sel_vec]

@@

    # month cols
    x$Month <- format(x$Date, '%m')

@@

# aggregate by weekly, monthly, seasonal categories
agg_sum <- llply(names(met_sub), 
  .fun = function(x){

    station <- gsub('_.*$', '', x)
    x <- met_sub[[x]]

@@

    # melt by weekly, monthly, seasonal cats
    # change here for cats to includes
    x <- melt(x, measure.var = c('Month'),
      id.var = c('Date', met_cols)
      )

    agg_res <- dlply(x,
      .var = 'variable', 
      .fun = function(y){

@@

          tmp <- summarySE(y, measurevar = met, groupvars = 'value',
            narm = T) 
          names(tmp)[names(tmp) %in% met] <- 'mean'
          tmp$var <- met
          out[[met]] <- tmp

@@

        # combine metabolism categories
        out <- do.call('rbind', out)

@@

    # combine time categories
    agg_res <- agg_res[[1]]

@@

    agg_res$station <- station

@@

to_plo <- do.call('rbind', agg_sum)

# reassign factor labels
to_plo$value <- factor(to_plo$value, levels = c('01', '02', '03', '04',
  '05', '06', '07', '08', '09', '10', '11', '12'), 
  labels = c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11',' 12')
  )
to_plo$var <- factor(to_plo$var, levels = c('Pg', 'Rt', 'NEM'), 
  labels = c('Pg', 'Rt', 'NEM'))
to_plo$sub_var <- factor(to_plo$sub_var, levels = c('dtd', 'obs'), 
  labels = c('Filtered', 'Observed'))
to_plo$station <- factor(to_plo$station, 
  levels = c('ELKVM', 'PDBBY', 'RKBMB', 'SAPDC'),
  labels = c('Elkhorn Slough', 'Padilla Bay', 'Rookery Bay', 
    'Sapelo Island')
  )

# remove may from RKB, lots of missing values
# remove may from Rookery Bay, lots of missing data
to_plo[to_plo$station %in% 'Rookery Bay'  & to_plo$value %in% '5', c('mean', 'sd', 'se', 'ci')] <- NA

@@

ylab <- expression(paste('g ', O [2], ' ', m^-2, d^-1))
p <- ggplot(to_plo, aes(x = factor(value), y = mean, group = sub_var,
    colour = sub_var)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_line() +
  geom_point() + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
    width=.3) +
  facet_grid(station ~ var, scales = 'free') +
  theme_bw() +
  scale_y_continuous(ylab) + 
  scale_x_discrete(name = element_blank()) +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    plot.margin= unit(rep(0, 4), "lines"),
    axis.text = element_text(size = 8)
    )

print(p)

@@

#   .progress = 'tk',

@@

#     # add month column
#     dat_in$month <- strftime(dat_in$Date, '%m')

@@

#     do_obs <- ddply(
#       dat_in, 
#       .variable = c('month'), 
#       .fun = function(x) with(x, cor.test(DO_obs, Tide)$estimate)

@@

#     do_dtd <- ddply(
#       dat_in, 
#       .variable = c('month'), 
#       .fun = function(x) with(x, cor.test(DO_nrm, Tide)$estimate)

@@

#     dat_in$month <- strftime(dat_in$Date, '%m')

@@

@@

#     # NA if error is returned in correlation
#     erf<- function(e) NA
#     met_cor <- ddply(
#         dat_in, 
#         .variable = c('month'), 

@@

#           with(x, {c(
#             Pg_obs = tryCatch(cor.test(Pg, sunrise)$estimate, error = erf),
#             Rt_obs = tryCatch(cor.test(Rt, sunset)$estimate, error = erf),
#             NEM_obs = tryCatch(cor.test(NEM, daytot)$estimate, error = erf),
#             Pg_dtd = tryCatch(cor.test(Pg_dtd, sunrise)$estimate, error = erf),
#             Rt_dtd =  tryCatch(cor.test(Rt_dtd, sunset)$estimate, error = erf),
#             NEM_dtd = tryCatch(cor.test(NEM_dtd, daytot)$estimate, error = erf)
#           )})

@@

@@

#     names(met_cor) <- gsub('\\.cor$', '', names(met_cor))

@@

#     res_sum <- data.frame(met_cor, do_obs = do_obs$cor, do_dtd = do_dtd$cor)

@@

#     # add column for sim name
#     res_sum$L1 <- nm

@@

# cor_res <- do.call('rbind', cor_res)
# row.names(cor_res) <- 1:nrow(cor_res)

@@

# cor_res$site <- gsub('_wtreg_[0-9]*$', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_', '', cor_res$L1))

@@

# cor_res <- melt(cor_res, measure.var = c('Pg_obs', 'Rt_obs', 'NEM_obs', 'Pg_dtd', 'Rt_dtd', 'NEM_dtd', 'do_obs', 'do_dtd'))

@@

# cor_res$sub_var <- gsub('^.*_', '', cor_res$variable)

@@

@@

# subset metab estimates by window widhts for each case study
load('case_grds.RData')
sel_vec <- llply(
  casewins, 
  .fun = function(x) with(case_grds, which(dec_time == x[[1]] & hour == x[[2]] & Tide == x[[3]]))
)
sel_vec <- paste0(names(casewins), '_wtreg_', unlist(sel_vec))

cor_res <- cor_res[cor_res$L1 %in% sel_vec, ]

# make wide form, take monthly averages of correlations
to_tab <- dcast(cor_res, site + sub_var ~ var, value.var = 'value', 
  fun.aggregate = function(x) mean(x, na.rm = T))

@@

# combine both tables
tab <- to_tab
rows <- as.character(tab$site)
tab <- form_fun(tab[, -c(1:2)])

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after (filtered) filtering with weighted regression.  Values are averages of monthly correlations.  \\ac{DO} values are correlated with predicted tidal height at each observation, whereas metabolism estimates are correlated with mean tidal height change between observations during day, night, or total day periods for production, respiration, and net metabolism, respectively.'

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism'

@@

% case study metabolism results, including perc anom
<<case_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# # metab estimates for each wtreg
# load('met_ls.RData')
# 
# met_comp <- ldply(met_ls, function(x){
#   
#   # detided
#   anoms <- anoms.fun(x, pgvar = 'Pg_dtd', rtvar = 'Rt_dtd')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg_dtd', 'Rt_dtd', 'NEM_dtd')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   dtd <- rbind(anoms, sums)
#   dtd$X1 <- gsub('_dtd', '', dtd$X1)
#   dtd$Input <- 'Detided'
#   
#   # observed
#   anoms <- anoms.fun(x, pgvar = 'Pg', rtvar = 'Rt')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg', 'Rt', 'NEM')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   obs <- rbind(anoms, sums)
#   obs$Input <- 'Observed'  
#   
#   # output
#   out <- rbind(dtd, obs)
#   names(out) <- c('Metab', 'Metric', 'Value', 'Input')
#   
#   return(out)
#   
#   })
# 
# save(met_comp, file = 'met_comp.RData')

@@

# subset metab estimates by window widths for each case study
load('case_grds.RData')
sel_vec <- llply(
  casewins, 
  .fun = function(x) with(case_grds, which(dec_time == x[[1]] & hour == x[[2]] & Tide == x[[3]]))
)
sel_vec <- paste0(names(casewins), '_wtreg_', unlist(sel_vec), '.RData')

met_comp <- met_comp[met_comp$.id %in% sel_vec, ]

@@

# make columns as factors for correct row, column order w/ dcast
to_tab$Input <- factor(to_tab$Input, levels = c('Observed', 'Detided'), labels = c('Observed', 'Filtered'))
to_tab$Metab <- factor(to_tab$Metab, levels = c('Pg', 'Rt', 'NEM'))
to_tab$Metric <- factor(to_tab$Metric, levels = c('Avg', 'se', 'Anom'))

@@

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism' 
latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = unique(to_tab$Site),
  n.rgroup = rep(2, 4),
  cgroup = c('Pg\\textsuperscript{\\textit{a}}', 'Rt', 'NEM'),
  n.cgroup = c(3, 3, 2),
  rowname = rows,
  colheads=c(rep(c('Mean','Std. Err.', 'Anom'),2), c('Mean', 'Std. Err.')),
  label = 'tab:case_res'
  )
@

\clearpage
